% !TeX spellcheck = en_US
\section{Installation}\label{section:install}

Application supports Windows, Linux and Mac operating systems. It requires Java 10 JRE or JDK to be installed. The newest version of Java can be downloaded here:\\ \href{http://www.oracle.com/technetwork/java/javase/downloads/index.html}{http://www.oracle.com/technetwork/java/javase/downloads/index.html}


RUDE application doesn't require installation. You simply need to download archived application and extract it to some directory. You can download it from here:\\ \href{http://www.cs.put.poznan.pl/mszelag/Software/ruleRank/ruleRank.html}{http://www.cs.put.poznan.pl/mszelag/Software/ruleRank/ruleRank.html}\newline

\textbf{Archive content description:}
\begin{itemize}
	\item \textbf{data directory} - it contains configuration files, see \hyperref[section:data-config]{Data configuration}
	\item \textbf{workspace directory} - it is default directory for storing all files related to experiments. It also contains some example experiments with result files.
	\item \textbf{readme.txt} - it contains information about requirements and running application
	\item \textbf{RuleRank jar file} - it contains compiled sources for this application
	\item \textbf{run.* files} - files which will run application after double click. Run files were prepared for each supported operating system.
\end{itemize}

You can run application by double clicking on respective run file. It will open console/terminal and run UI application. In case of any problems with running RUDE, error logs will be displayed in console/terminal. If you encounter any errors, it is recommended to execute run file in cmd/powershell or terminal, instead of double clicking. It will not close console/terminal after application exit.


\vfill\newpage